AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
Remove duplicate figure. #42

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/website.png}
    \caption{Example view of algorithm ranking results in DORA web interface
    for planetary dataset.}
    \label{fig:website}
\end{figure}

@@

\section{Results}
The experimental setup for each dataset was to fit or train a model for
each ranking algorithm using a larger unlabeled dataset and then apply 
the models to compute the outlier scores for a smaller test dataset for which
labels of known outliers were available (Table \ref{tab:datasets}). 
For each test set, we created a plot of the number of known/true outliers 
detected out of the top $N$ selections. We also 
reported the Mean Discovery Rate (MDR) in the legend
for each algorithm to give a quantitative comparison of the curves that could
be comparable across the datasets. We defined MDR as:
\begin{equation}
MDR = \frac{\sum^{N_s}_{i=1} n_i}{\sum^{N_s}_{i=1} s_i}
\end{equation}
where $i \in [1, N_s]$ is the selection index,
 $N_s$ is the total number of selections,
 $s_i$ is the number of selections made up to index $i$,
 and $n_i$ is the number of known outliers (true positives)
among $s_i$ selections.
We also reported the precision at $N=n_{outlier}$ for each test set where
$n_{outlier}$ is the number of known outliers, i.e.,  the precision obtained 
when the number of selections is the same as the total number of outliers. 
Precision at $N$ is the number of true outliers divided by the number of 
selections $N$~\citep{campos2016evaluation}.
Table~\ref{tab:faw_results} compares the precision at $N=n_{outlier}$ for
each dataset and ranking algorithm. \todo{Random desc by Jake, please edit}
Metrics for random selection are calculated
using the expected value of $n_i$ for $i$ random selections:
\begin{equation}
\mathbf{E}[n_i, i \in[1, N_s]] = \frac{\sum^i_{j=0} {n_{outlier}\choose j} {D-n_{outlier}\choose i-j} j}{{D\choose i}}
\end{equation}

>>>>

@@

\section{Results}
The experimental setup for each dataset was to fit or train a model for
each ranking algorithm using a larger unlabeled dataset and then apply 
the models to compute the outlier scores for a smaller test dataset for which
labels of known outliers were available (Table \ref{tab:datasets}). 
For each test set, we created a plot of the number of known/true outliers 
detected out of the top $N$ selections. We also 
reported the Mean Discovery Rate (MDR) in the legend
for each algorithm to give a quantitative comparison of the curves that could
be comparable across the datasets. We defined MDR as:
\begin{equation}
MDR = \frac{\sum^{N_s}_{i=1} n_i}{\sum^{N_s}_{i=1} s_i}
\end{equation}
where $i \in [1, N_s]$ is the selection index,
 $N_s$ is the total number of selections,
 $s_i$ is the number of selections made up to index $i$,
 and $n_i$ is the number of known outliers (true positives)
among $s_i$ selections.
We also reported the precision at $N=n_{outlier}$ for each test set where
$n_{outlier}$ is the number of known outliers, i.e.,  the precision obtained 
when the number of selections is the same as the total number of outliers. 
Precision at $N$ is the number of true outliers divided by the number of 
selections $N$~\citep{campos2016evaluation}.
Table~\ref{tab:faw_results} compares the precision at $N=n_{outlier}$ for
each dataset and ranking algorithm. 
We calculated a random selection baseline which we refer to as ``Theoretical
Random'' using the expected value of $n_i$ for $i$ random selections:
\begin{equation}
\mathbf{E}[n_i, i \in[1, N_s]] = \frac{\sum^i_{j=0} {n_{outlier}\choose j} {D-n_{outlier}\choose i-j} j}{{D\choose i}}
\end{equation}
